Variants on the Flight and Maintenance Planning problem

### 2018-08-27 latex/notes/model/model.tex
small changes in model

    \begin{tabular}{p{8mm}p{167mm}}
        $H_j$             & amount of resource time required by task $j$. \\
        $R_j$             & number of resources required by task $j$. \\
        $MT_j$            & minimum number of consecutive periods a resource can be assigned to task $j$. \\
        % $aut_i$           & maximal absolute usage time for resource $i$. \\
        % $aet_i$           & maximal absolute elapsed time for resource $i$. \\
        $M$               & maintenance duration in number of periods. \\
        $M^{max}$         & maximum number of simultaneous maintenance operations. \\
        % $E$               & remaining elapsed time after a maintenance. \\
        $E^{M}$         & maximum number of periods between two consecutive maintenances. \\
        $E^{m}$         & minimum number of periods between two consecutive maintenances. \\
        $H$               & remaining usage time after a maintenance. \\
        % $S$               & Storage duration in number of periods. \\
        % $W_1$             & weight of the first objective in the objective function. \\
        % $W_2$             & weight of the second objective in the objective function. \\
        % $N_t$             & number of resources in already-planned maintenances in period $t$ at the beginning of the planning horizon.\\
        % $D_t$             & number of resources to be assigned in total in period $t$. \\
        $AK_{kt}$         & maximum number of resources in cluster $k$ that can be simultaneously under maintenance at period $t$.\\
        $Rut^{Init}_{i}$  & remaining usage time for resource $i$ at the start of the planning horizon. \\
        $Ret^{Init}_{i}$  & remaining elapsed time for resource $i$ at the start of the planning horizon. \\
        $A^{init}_{jti}$  & =1 if resource $i \in \mathcal{I}$ has task $j$ pre-assigned in period $t$. \\
        % $Ret^{Init}_{sum}$& sum of remaining elapsed times at the start of the planning horizon. \\
        % $Rut^{Init}_{sum}$& sum of remaining elapsed time at the start of the planning horizon. \\
    \end{tabular}

@@

    \begin{tabular}{p{8mm}p{167mm}}
        $a_{jti}$   &  =1 if task $j \in J$ in period $t \in \mathcal{T}_j$ is realized with resource $i \in \mathcal{I}_j$, 0 otherwise. \\  
        $a^s_{jti}$ &  =1 if resource $i$ starts a new assignment to task $j$ in period $t$. If $a_{jti} = 1$ and $a_{j(t-i)} = 0$. \\  
        $m_{it}$    &  =1 if resource $i \in I$ starts a maintenance operation in period $t \in \mathcal{T}$, 0 otherwise. \\
        % $s_{it}$    &  =1 if resource $i \in I$ starts a storage operation in period $t \in \mathcal{T}$, 0 otherwise. \\
        $rut_{it}$  &  remaining usage time (continuous) for resource $i \in I$ at the end of period $t \in \mathcal{T}$. \\  
        % $ret_{it}$  &  remaining elapsed time (integer) for resource $i \in I$ at the end of period $t \in \mathcal{T}$. \\  
        % $u_{max}$   &  maximal number (integer) of unavailable resources in any period. \\
        % $m_{max}$   &  maximal number (integer) of resources in maintenance in any period. \\
    \end{tabular}

@@

    The following constraints are used in the model:       
    \begin{align}
        % maximum capacity1:
        % & \sum_{t' \in \mathcal{T}^{s}_t} \sum_{i \in \mathcal{I}} m_{it'} + N_t \leq m_{max}
        %   & t \in \mathcal{T} \label{eq:capacity1}\\
        & \sum_{t \in \mathcal{T}, i \in \mathcal{I}} m_{it} \leq M^{max} \label{eq:capacity1}\\
        % availability
       % & \sum_{t' \in \mathcal{T}^{s}_t} \sum_{i \in \mathcal{I}} m_{it'} + N_t + D_t\leq u_{max} 
       %  &t \in \mathcal{T} \label{eq:avalaibility1}\\
        % min assignments:
        & \sum_{i \in \mathcal{I}_j} a_{jti} = R_j
                & j \in \mathcal{J}, t \in \mathcal{T}_j  \label{eq:taskres}\\
        % just doing one thing at any given time:
        & \sum_{t' \in \mathcal{T}^{s}_t} m_{it'} + \sum_{j \in \mathcal{J}_t \cap \mathcal{O}_i} a_{jti} \leq 1 
                & t \in \mathcal{T}, i \in \mathcal{I} \label{eq:state}
    \end{align}

@@

    The minimum and maximum elapsed time are defined by (\ref{eq:ret_min}) and (\ref{eq:ret_max}) respectively. Constraints (\ref{eq:ret_min}) guarantee that if a maintenance is done in some period $t$, we know that it cannot be done in the immediately consecutive $t' \in \mathcal{T}^{m}_t$ periods. Constraints (\ref{eq:ret_max}) guarantee that, if we have a maintenance in period $t$, we need to start at least one maintenance among periods $t' \in \mathcal{T}^{M}_t$. Constraints (\ref{eq:ret_min_init}) and (\ref{eq:ret_max_init}) control the minimum and maximum remaining elapsed time at the beginning of the planning period, respectively. They follow the same rules as the previous constraints for the particular case of the start of the planning horizon.

>>>>

    \begin{tabular}{p{8mm}p{167mm}}
        $H_j$             & amount of resource time required by task $j$. \\
        $R_j$             & number of resources required by task $j$. \\
        $MT_j$            & minimum number of consecutive periods a resource can be assigned to task $j$. \\
        % $aut_i$           & maximal absolute usage time for resource $i$. \\
        % $aet_i$           & maximal absolute elapsed time for resource $i$. \\
        $M$               & maintenance duration in number of periods. \\
        $M^{max}$         & maximum number of simultaneous maintenance operations. \\
        % $E$               & remaining elapsed time after a maintenance. \\
        $E^{M}$         & maximum number of periods between two consecutive maintenances. \\
        $E^{m}$         & minimum number of periods between two consecutive maintenances. \\
        $H$               & remaining usage time after a maintenance. \\
        % $S$               & Storage duration in number of periods. \\
        % $W_1$             & weight of the first objective in the objective function. \\
        % $W_2$             & weight of the second objective in the objective function. \\
        $N_t$             & number of resources in already-planned maintenances in period $t$.\\
        % $D_t$             & number of resources to be assigned in total in period $t$. \\
        $AK_{kt}$         & maximum number of resources in cluster $k$ that can be simultaneously under maintenance at period $t$.\\
        $Rut^{Init}_{i}$  & remaining usage time for resource $i$ at the start of the planning horizon. \\
        $Ret^{Init}_{i}$  & remaining elapsed time for resource $i$ at the start of the planning horizon. \\
        $A^{init}_{jti}$  & =1 if resource $i \in \mathcal{I}$ has task $j$ pre-assigned in period $t$. \\
        % $Ret^{Init}_{sum}$& sum of remaining elapsed times at the start of the planning horizon. \\
        % $Rut^{Init}_{sum}$& sum of remaining elapsed time at the start of the planning horizon. \\
    \end{tabular}

@@

    \begin{tabular}{p{8mm}p{167mm}}
        $a_{jti}$   &  =1 if task $j \in J$ in period $t \in \mathcal{T}_j$ is realized with resource $i \in \mathcal{I}_j$, 0 otherwise. \\  
        $a^s_{jti}$ &  =1 if resource $i$ starts a new assignment to task $j$ in period $t$. If $a_{jti} = 1$ and $a_{j(t-1)i} = 0$. \\  
        $m_{it}$    &  =1 if resource $i \in I$ starts a maintenance operation in period $t \in \mathcal{T}$, 0 otherwise. \\
        % $s_{it}$    &  =1 if resource $i \in I$ starts a storage operation in period $t \in \mathcal{T}$, 0 otherwise. \\
        $rut_{it}$  &  remaining usage time (continuous) for resource $i \in I$ at the end of period $t \in \mathcal{T}$. \\  
        % $ret_{it}$  &  remaining elapsed time (integer) for resource $i \in I$ at the end of period $t \in \mathcal{T}$. \\  
        % $u_{max}$   &  maximal number (integer) of unavailable resources in any period. \\
        % $m_{max}$   &  maximal number (integer) of resources in maintenance in any period. \\
    \end{tabular}

@@

    The following constraints are used in the model:       
    \begin{align}
        % maximum capacity1:
        & \sum_{t' \in \mathcal{T}^{s}_t} \sum_{i \in \mathcal{I}} m_{it'} + N_t \leq M^{max}
          & t \in \mathcal{T} \label{eq:capacity1}\\
        % & \sum_{t \in \mathcal{T}, i \in \mathcal{I}} m_{it} \leq M^{max} \label{eq:capacity1}\\
        % availability
       % & \sum_{t' \in \mathcal{T}^{s}_t} \sum_{i \in \mathcal{I}} m_{it'} + N_t + D_t\leq u_{max} 
       %  &t \in \mathcal{T} \label{eq:avalaibility1}\\
        % min assignments:
        & \sum_{i \in \mathcal{I}_j} a_{jti} = R_j
                & j \in \mathcal{J}, t \in \mathcal{T}_j  \label{eq:taskres}\\
        % just doing one thing at any given time:
        & \sum_{t' \in \mathcal{T}^{s}_t} m_{it'} + \sum_{j \in \mathcal{J}_t \cap \mathcal{O}_i} a_{jti} \leq 1 
                & t \in \mathcal{T}, i \in \mathcal{I} \label{eq:state}
    \end{align}

@@

    The minimum and maximum elapsed time are defined by (\ref{eq:ret_min}) and (\ref{eq:ret_max}) respectively. Constraints (\ref{eq:ret_min}) guarantee that if a maintenance is done in some period $t$, we know that another one cannot be done in the immediately consecutive $t' \in \mathcal{T}^{m}_t$ periods. Constraints (\ref{eq:ret_max}) guarantee that, if we have a maintenance in period $t$, we need to start at least one maintenance among periods $t' \in \mathcal{T}^{M}_t$. Constraints (\ref{eq:ret_min_init}) and (\ref{eq:ret_max_init}) control the minimum and maximum remaining elapsed time at the beginning of the planning period, respectively. They follow the same logic as constraints (\ref{eq:ret_min}) and (\ref{eq:ret_max}), respectively, for the particular case of the start of the planning horizon.
